---
title: "p8105_hw3_yh3429"
output: html_document
date: "2022-10-10"
---

#### **Load the data from the `p8015.datasets`**

```{r , message=FALSE}
library(tidyverse)
library(ggplot2)
library(p8105.datasets)
```




## Problem 1

#### Short description
In this instacart data, there are **1384,617** observations and **15** variables. The key variables include `order_id` `product_id` `user_id` `eval_set` `product_name` `department_id` `department` `aisle_id` `aisle` and so on. 
```{r}
data("instacart")
```

#### How many aisles are there, and which aisles are the most items ordered from?

There are **134** aisles and `fresh_vegetables`are the most items ordered, with **150,609** ordered items. 
```{r}
instacart %>%  group_by (aisle) %>% summarize(n_obs = n()) %>% 
  mutate(aisle_ranking = min_rank(n_obs))
```
#### Make a plot that shows the number of items ordered in each aisle, limiting this to aisles with more than 10000 items ordered. 
```{r}
aisles_plot=
  instacart %>% 
  group_by (aisle) %>% 
  summarize(n_obs = n()) %>% 
  filter(n_obs >10000) %>% 
ggplot (aes(x= aisle, y=n_obs))+geom_point()+labs (x="aisle names" , y="numbers of itmes", title = "plot of the number of items ordered in each aisle")+  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))

ggsave("aisles_plot.pdf")
```

#### Make a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”. Include the number of times each item is ordered in your table.
```{r}
 instacart %>% 
  select (aisle, everything()) %>% 
  subset(aisle == "baking ingredients" ) 
  
```

#### Make a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week; format this table for human readers (i.e. produce a 2 x 7 table).
```{r}
 
 
```











## Problem 2

#### Load and tidy the data. Describe the resulting dataset.

There are **6** variables and **50,400** observations in the resulting dataset.The key variables include `week` `day_id` `day` `activity_time` `activity_counts` and `day_of_week`.
```{r}
accel = read_csv("./data/accel_data.csv") %>% 
  janitor::clean_names() %>% 
  pivot_longer( activity_1: activity_1440,
                names_to = "activity_time",
                names_prefix = "activity_",
                values_to = "activity_counts" ) %>% 
  mutate((day_of_week= case_when(
    startsWith(day, "Mon") ~ "Weekday",
    startsWith(day, "Tu") ~"Weekday",
    startsWith(day, "We")~"Weekday",
    startsWith(day, "Thu")~"Weekday",
    startsWith(day, "Fri")~"Weekday",
    startsWith(day, "S")~"Weekend")
  ) ) %>% 
  mutate(day = as.factor(day), activity_time = as.numeric(activity_time)) %>% 
  mutate(day = forcats::fct_relevel(day,c("Monday", "Tuesday", "Wednesday","Thursday", "Friday", "Saturday", "Sunday") ) )

accel
```
#### Create a total acitivty variable and a table.Are any trends apparent?

 
```{r}
total_activity=
  accel %>% group_by(week, day) %>% summarise(total_activity= sum(activity_counts)) %>%  knitr::kable()

total_activity
```
*Based on looking at the table, there aren't any apparent trends presenting.*


####  Make a single-panel plot. Describe in words any patterns.
```{r}
accel %>% 
ggplot(aes(x = activity_time, y = activity_counts, group= day)) +
 geom_point(aes(color = day), alpha=0.5)+
    labs(
        x = "Times (hours)",
        y = "Activity counts",
        title = "The 24-hour activity time courses for each day",  color = "Day" )+
  scale_x_continuous(
    breaks = c(0,180,360,540,720,900,1080,1260,1440),
    labels = c("00:00","3:00","6:00","9:00",
               "12:00","15:00","18:00","21:00","24:00")
  )
    
```
*Based on this graph, this 63 year-old male patient with BMI 25 had a relatively higher activity counts on Friday between 19:00 hour and 22:00 hour. In addition, he also had a relatively higher activity counts on Sunday between 11:00 hour and 12:00 hour. *









## Problem 3

```{r}
data("ny_noaa")

ny_noaa_tidy =
  ny_noaa %>% 
  janitor::clean_names() %>%
  separate(date, into = c("year", "month", "day")) %>%
  mutate(prcp = paste(prcp, "0.1mm"),
         snow = paste(snow, "mm"),
         snwd = paste(snwd, "mm"),
         tmax = paste(tmax, "0.1Celsius"),
         tmin = paste(tmin, "0.1Celsius"))

```


